Meta analysis of differential expression results from AMP-AD (Control vs AD, reprocessed RNASeq)

### 2017-05-17 code/Rmd/MetaAnalysis.Rmd

library(Vennerable)
library(colorfulVennPlot)
library(rmeta)

@@

# Download celltype specific genesets from synapse
load(synGet('syn9818080')@filePath)
all.used.ids = c(all.used.ids, 'syn9818080')

GeneSets = c(GeneSets.Enrichr, 
             list(CellTypeMarkers = CellTypeList,
                  AD = AD))

GeneSets = do.call(c, GeneSets)
```

>>>>

library(Vennerable)
library(colorfulVennPlot)
library(rmeta)
library(xlsx)

@@

# Download cell type markers from synapse (list from GSE73721 by Mariet)
load(synGet('syn9818080')@filePath)
all.used.ids = c(all.used.ids, 'syn9818080')

GeneSets = c(list(CellTypeMarkers = CellTypeList,
                AD = AD),
                GeneSets.Enrichr)
```
